---
title: "Cabbages"
author: "Rashonda Weathersby"
date: "02-04-21"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(veggy,aes(x=Cult,y=VitC))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
 
 
 The boxplot shows that c52 is more than c39. C52 has over 80, and the c 39 is between 65 and 70.   
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
favstats(VitC~Cult,data=veggy)
```
The table shows that c52 average Vitamin c units was 64.5, as the c39 was only average 51.0 unit. 


## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
t.test(VitC~Cult,data=veggy)
```
 The hypotheses concluded that the vitamin c units are equal however, according to th p-value of .00000003405,the number is so small, we can conclude that the hypotheses is a null hypothese.   
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

We can conclude that the cultivation method results that there is a greater vitamin content in c52 then there is in c39.  
